%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Talks}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvtalks}
  \cvtalk
  {Kneser Graphs are Hamiltonian}
  {based on [\hyperlink{paper8}{8}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{Annual meeting of the German Mathematical Society, 2023.} \hfill \cvreferencewho{Ilmenau, Germany} 
      \item \descriptionstyle{Graph Theory Seminar, 2023.} \hfill \cvreferencewho{TU Ilmenau, Germany} 
    \end{cvitems}
  }
  \cvtalk
  {Traversing Combinatorial 0/1-Polytopes via Optimization}
  {based on [\hyperlink{paper11}{11}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{Theory of Computing Seminar, 2023.} \hfill \cvreferencewho{Charles U., Czechia}
      \item \descriptionstyle{Computer Science Colloquium, 2023.} \hfill \cvreferencewho{Queens College CUNY, USA}
      \item \descriptionstyle{64th Symposium on the Theory of Computing, 2023.} \hfill \cvreferencewho{Santa Cruz, USA}
      \item \descriptionstyle{Algorithms and Complexity noon seminar, 2023.} \hfill \cvreferencewho{MPI for Informatics, Germany}
      \item \descriptionstyle{3rd Workshop on Combinatorial Reconfiguration, 2023.} \hfill \cvreferencewho{U. of Paderborn, Germany}
      \item \descriptionstyle{Beyond Permutahedra and Associahedra workshop, 2023.} \hfill \cvreferencewho{Weissensee, Austria} 
      \item \descriptionstyle{DISC seminar, 2022.} \hfill \cvreferencewho{U. Adolfo Ibañez, Chile} 
      \item \descriptionstyle{AGCO seminar, 2022.} \hfill \cvreferencewho{U. de Chile, Chile}
      \item \descriptionstyle{DISCOGA seminar, 2022.} \hfill \cvreferencewho{TU Berlin, Germany}
    \end{cvitems}
  }
  \cvtalk
  {The Hamilton Compression of Highly Symmetric Graphs}
  {based on [\hyperlink{paper8}{8}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{Graph Theory Seminar, 2022.} \hfill \cvreferencewho{U. de Chile, Chile} 
    \end{cvitems}
  }
  \cvtalk
  {Efficient Generation of Rectangulations via Permutation Languages}
  {based on [\hyperlink{paper4}{4}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{Theory of Combinatorial Algorithms Mittagsseminar, 2022.} \hfill \cvreferencewho{ETH Zürich, Switzerland}
    \end{cvitems}
  }
  \cvtalk
  {All your Bases are Belong to Us}
  {based on [\hyperlink{paper7}{7}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{11th International Conference on Fun with Algorithms, 2022.} \hfill \cvreferencewho{Favignana, Italy} 
    \end{cvitems}
  }
  \cvtalk
  {Greedy Generation for Hamilton Paths in Rectangulations, Elimination Trees, and Matroids}
  {based on [\hyperlink{paper4}{4},\hyperlink{paper5}{5},\hyperlink{paper7}{7}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{Institute of Geometry seminar, 2022.} \hfill \cvreferencewho{TU Graz, Austria}
    \end{cvitems}
  }
  \cvtalk
  {Greedily Generating All Bases of a Matroid by Base Exchanges}
  {based on [\hyperlink{paper7}{7}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{Applied Mathematics Noon Lecture, 2022.} \hfill \cvreferencewho{Charles U., Czechia}
    \end{cvitems}
  }
  \cvtalk
  {On a Combinatorial Generation Problem of Knuth}
  {based on [\hyperlink{paper3}{3}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{CS Theory seminar, 2022.} \hfill \cvreferencewho{Williams College, USA} 
    \end{cvitems}
  }
  \cvtalk
  {Efficient Generation of Elimination Trees and Graph Associahedra}
  {based on [\hyperlink{paper5}{5}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{33rd ACM-SIAM Symposium on Discrete Algorithms, 2022.} \hfill \cvreferencewho{Alexandria, USA}
      \item \descriptionstyle{IOL \& DISCOGA seminar, 2021.} \hfill \cvreferencewho{TU Berlin \& ZIB, Germany}
      \item \descriptionstyle{Discrete Mathematics Mittagsseminar, 2021.} \hfill \cvreferencewho{TU Berlin, Germany}
    \end{cvitems}
  }
  \cvtalk
  {Eficient Generation of Rectangulations and Elimination Trees}
  {based on [\hyperlink{paper4}{4},\hyperlink{paper5}{5}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{Séminaire de Combinatoire du Plateau de Saclay, 2021.} \hfill \cvreferencewho{U. Paris-Saclay, France}
    \end{cvitems}
  }
  \cvtalk
  {Eficient Generation of Rectangulations via Permutation Languages}
  {based on [\hyperlink{paper4}{4}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{Applied Mathematics Noon Lecture, 2021.} \hfill \cvreferencewho{Charles U., Czechia}
      \item \descriptionstyle{Workshop on Combinatorial Reconfiguration, 2021.} \hfill \cvreferencewho{U. of Glasgow, Scotland}
      \item \descriptionstyle{37th International Symposium on Computational Geometry, 2021.} \hfill \cvreferencewho{U. of Buffalo, USA}
      \item \descriptionstyle{IOL \& DISCOGA seminar, 2020.} \hfill \cvreferencewho{TU Berlin, Germany}
    \end{cvitems}
  }
  \cvtalk
  {Pattern-Avoiding Permutations and Rectangulations}
  {based on [\hyperlink{paper4}{4}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{19th International Conference on Permutation Patterns, 2021.} \hfill \cvreferencewho{U. of Strathclyde, Scotland}
    \end{cvitems}
  }
  \cvtalk
  {Greedy Strategies for Exhaustive Generation}
  {survey talk}
  {
    \begin{cvitems}
      \item \descriptionstyle{IOL \& DISCOGA seminar, 2021.} \hfill \cvreferencewho{TU Berlin \& ZIB, Germany}
    \end{cvitems}
  }
  \cvtalk
  {Symmetric Hamilton Cycles on Symmetric Graphs}
  {based on [\hyperlink{paper3}{3}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{Berlin Mathematical School conference, 2021.} \hfill \cvreferencewho{Berlin, Germany}
      \item \descriptionstyle{Graph Theory seminar, 2020.} \hfill \cvreferencewho{U. de Chile, Chile}
    \end{cvitems}
  }
  \cvtalk
  {On the Two-Dimensional Knapsack Problem for Convex Polygons}
  {based on [\hyperlink{paper2}{2}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{AGCO seminar (available \href{https://drive.google.com/file/d/1fCyPOUXSjNq0gQHgnS0xwQIUWU-IK3b_/view}{here}), 2020.} \hfill \cvreferencewho{U. de Chile, Chile}
      \item \descriptionstyle{47th International Colloquium on Automata, Languages and Programming (\href{https://youtu.be/0q_GryBSoOM}{youtube}), 2020.} \hfill \cvreferencewho{U. des Saarlandes, Germany}
      \item \descriptionstyle{COGA seminar, 2020.} \hfill \cvreferencewho{TU Berlin, Germany}
    \end{cvitems}
  }
  \cvtalk
  {How to Pack Objects into a Knapsack}
  {based on [\hyperlink{paper2}{2}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{Berlin Mathematical School Conference, 2020.} \hfill \cvreferencewho{Berlin, Germany}
    \end{cvitems}
  }
  \cvtalk
  {Combinatorial Gray Codes and Permutations}
  {survey talk}
  {
    \begin{cvitems}
      \item \descriptionstyle{Graph Theory seminar, 2019.} \hfill \cvreferencewho{U. de Chile, Chile}
    \end{cvitems}
  }
  \cvtalk
  {The Minimum Cost Query Problem on Matroids with Uncertainty Areas}
  {based on [\hyperlink{paper1}{1}]}
  {
    \begin{cvitems}
      \item \descriptionstyle{COGA Seminar, 2019.} \hfill \cvreferencewho{TU Berlin, Germany}
      \item \descriptionstyle{46th International Colloquium on Automata, Languages and Programming, 2019.} \hfill \cvreferencewho{U. of Patras, Greece}
      \item \descriptionstyle{DISC seminar, 2019.} \hfill \cvreferencewho{U. Adolfo Ibañez, Chile}
      \item \descriptionstyle{14th Summer School in Discrete Mathematics, 2019.} \hfill \cvreferencewho{Valparaíso, Chile}
      \item \descriptionstyle{Chilean Mathematical Society annual encounter, 2018.} \hfill \cvreferencewho{U. de O'Higgins, Chile}
      \item \descriptionstyle{Mathematical Engineering annual encounter, 2018.} \hfill \cvreferencewho{U. de Concepción, Chile}
      \item \descriptionstyle{AGCO seminar, 2018.} \hfill \cvreferencewho{U. de Chile, Chile}
    \end{cvitems}
  }
\end{cvtalks}